Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-10 paper/galsize_paper.tex
Improved clarity of discussion in 5.1 of color-dependent results

Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, can be naturally explained within the same framework.  For example, it is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much more strongly than  blue galaxies \citep[e.g.,][]{zehavi_etal11}. Samples of red (blue) galaxies with stellar masses of $\mstar\sim 10^{10}\ M_\odot$ are dominated by satellite (central) galaxies, and splitting by size {\em within} such samples no longer corresponds to the split into satellite- and central-dominated samples. In this case, the $\rvir$-based size model predicts that splitting by size {\em does} correspond to splitting by halo mass $\rhalf\propto\rvir\propto\mhalo^{1/3},$ and therefore that large galaxies should be somewhat more clustered than the small ones. That is, the $\rvir-$based model predicts that $\rhalf-$dependent clustering should be reversed for color-selected samples, and that the magnitude of the dependence should be significantly weaker due to weak dependence of virial radius on halo mass, and weak dependence of clustering on halo mass in this regime.

While we consider such an explanation plausible, and even likely, a conclusive confirmation requires proper forward modeling of size and color jointly. Such an effort is strongly motivated by our results, but is beyond the scope of the present work.

>>>>

Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, can be naturally explained by the same principles.  It is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}, and so blue galaxies have a small satellite fraction, while red galaxies have a large fraction of satellites that occupy high-mass halos; accordingly, red galaxies cluster much more strongly than blue galaxies \citep[e.g.,][]{zehavi_etal11}. Pre-selecting galaxy samples by color then naturally restricts the impact of satellites on size-dependent clustering. For blue galaxies, the reason traces to the small value of $F_{\rm sat};$ for red galaxies, the reason traces to the limited dynamic range of halo masses occupied by the satellites. With the impact of satellites reduced, the relative clustering of centrals becomes more important. In the limit that size-dependent clustering is dominated by centrals, the $\rvir$-based size model predicts that large galaxy samples should be (weakly) more clustered than small ones, because $\rhalf\propto\rvir\propto\mhalo^{1/3}.$ This is the trend seen in the clustering measurements shown in Figure \ref{fig:colorclustering}.

While we consider such an explanation plausible, and even likely, a conclusive confirmation requires proper forward modeling of size and color jointly. Such an effort is well motivated by our results, but is beyond the scope of the present work.
